The YUIMA Project: a Computational Framework for Simulation and Inference of Stochastic Differential Equations

### 2013-02-07 pkg/yuimadocs/inst/doc/JSS/article-new.Rnw
various update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@229 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

{\bf STEFANO: add comparison with other approx formulas}\par

>>>>

<<>>=
library(fExoticOptions)
LevyAsianApproxOption(TypeFlag = "c", S = xinit, SA = xinit, X = K, 
      Time = 1, time = 1, r = 0.0, b = 1, sigma = e)@price
TurnbullWakemanAsianApproxOption(TypeFlag = "c", S = xinit, SA = xinit, 
X = K, Time = 1, time = 1, r = 0.0, b = 1, sigma = e,tau=0)@price
@
{\bf STEFANO: add comparison with other approx formulas}\par
